Self-test prime dimensional EPR pairs with constant alphabet

### 2018-12-15 Draft/draft.tex
Honghao: added my progress on the main proof

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{EPR^{(#1)}}
\newcommand{\paulix}[1]{\sigma_x^{(#1)}}
\newcommand{\pauliz}[1]{\sigma_z^{(#1)}}
\newcommand{\G}[1]{G^{(#1)}}
\newcommand{\LS}{LS}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tpsi}{\tilde{\psi}}

@@

\title{Self-test EPR pair with constant alphabet}

@@

The main tool to understand linear system game is through its solution group over $\Z_d$.
\begin{definition}[Solution group over $\Z_d$ \cite{coladan2017}]
	For the linear system game associated with $Ax = b$ over $\Z_d$, its solution group $\Gamma(A,b,\Z_d)$ has 
	one generator for each variable and one relation for each equation and relations enforcing that the variables in the same
	equation commutes. The set of local commutativity relations is denoted by $R_c$ and defined by
	\begin{align}
		R_c := \set{ [x_i, x_j] |  A_{li} \neq 0 \neq A_{lj} \text{ for some } 1 \leq l \leq m}.
	\end{align}
	The set of constraint satisfaction relations is denoted by $R_{eq}$ and defined by.
	\begin{align}
		R_{eq} := \set{ \J^{-b(l)} \Pi_{i=1}^n  x_i^{A_{li}} | 1\leq l\leq m}
	\end{align}
	Then the solution group has presentation 
	\begin{align}
	\Gamma(A,b,\Z_d) := \ip{ \{x_i\}_{i=1}^n \cup \{\J\} : R_c \cup R_{eq} \cup \{ (x_i)^d, \J^d| 1 \leq i \leq n\}}. 
	\end{align}
\end{definition}
Note that the relations $(x_i)^d$ and $\J^d$ ensure that we have solutions over $\Z_d$.
Then the operator solution of $\Gamma(A,b,\Z_d)$ is given below.
\begin{definition}[Operator solution]
	An operator solution for the linear system game associated with $Ax =b$ over $\Z_d$ is a unitary representation
	$\tau$ of $\Gamma(A,b,\Z_d)$ such that $\tau(\J) = \omega_d\1$. A conjugate operator solution is a unitary 
	representation mapping $\J$ to $\overline{\omega_d}\1$.
\end{definition}
What has been established in Ref.\cite{cleve2017,coladan2017} is that we can construct a perfect strategy of a
linear system game from its operator solution and vice versa.
%========================================
\section{Components of $\G{d}$}
%========================================
Suppose we would like to self-test $\ket{\EPR{d}}$ with $\G{d}$, where $d$ is prime and has primitive root $2$.
Later we will see how to deal with general prime numbers and why there are infinitely many prime dimensional EPR pairs 
that can be self-tested by a variant of $\G{d}$.
%----------------------------------------------------------------
\subsection{The linear system game}
%----------------------------------------------------------------
The main component of $\G{d}$ is a linear system game $\LS$, whose solution group is derived from the qudit Pauli group,
which is defined as
\begin{align}
	\Pg_d = \langle x, z, \J : x^d = z^d = \J^d = e, zxz^{-1}x^{-1} = \J, x\J x^{-1}\J^{-1}= z\J z^{-1}\J^{-1} = e\rangle. 
\end{align}
The goal of our modification is to construct $\Pg_{\LS}$ which has implicit $d$-dependence.
We first introduce new generators $u_x$ and $u_z$ to $\Pg_d$, and replace the relation $x^d = z^d = e$ 
by the following relations
\begin{align}
\label{eq:sim}
	u_x x u_x = x^2, \quad
	u_z z u_z = z^2.
\end{align}
Consequently, the $d$ dependency of $\G{d}$ comes from constraints imposed by other components of the game,
\footnote{Figuring out what $a$ is will take us one step closer to resolving Artin's Conjecture\cite{murty1988}.}
but the alphabet sizes are determined by $\Pg_{\LS}$ and we will see why they are constant.
Next, we drop the relation $\J^d = e$ and make the value of $\J$ determined by $x$ and $z$ in the 
relation $xzx^{-1}z^{-1} = \J$.

It can be easily checked that $\paulix{d}$ and $\pauliz{d}$ can be extended to a representation of $\Pg_{\LS}$ 
where  $\paulix{d}$ and $\pauliz{d}$ are defined by
\begin{align}
	\paulix{d} = \sum_{i=0}^{d-1} \ketbra{i+1 \pmod{d} }{i}  \quad \quad
	\pauliz{d} = \sum_{i=0}^{d-1} \omega_d^i \ketbra{i}{i}.
\end{align}
Moreover, if $U_x\paulix{d}U_x^\dagger = (\paulix{d})^2$ and $U_z\pauliz{d}U_z^\dagger = (\pauliz{d})^2$,
we can verify that 
\begin{align}
	U_xU_z = \1 = U_zU_x,
\end{align}
Hence, we do not need both $u_x$ and $u_z$ as generators and we just need one of them.
In the end, we define $\Pg_{\LS}$ by
\begin{equation}
\begin{aligned}
	\Pg_{\LS} =  \langle x, z, u, \J :  &zxz^{-1}x^{-1} = \J, [x,\J]=[z,\J]=[u,\J] = e, \\
	&uxu^{-1} = x^2, u^{-1}zu = z^2 \rangle. 
\end{aligned}
\end{equation}
This group will be embedded in a solution group, $\Gamma(\LS)$, following Slofstra's embedding techniques.
The corresponding game $\LS$ has $n = 2351$ variables and $m= 1916$ equations.
See Appendix~\ref{sec:construct} for details.
%------------------------------------------------------------------------
\subsection{The extended weighted CHSH game}
%------------------------------------------------------------------------
The extended weighted CHSH game is added to make sure that some of Alice and Bob's observables have
eigenvalues $\omega_d$ and $\omega_d^{d-1}$.
The notation for the extended weighted CHSH game that enforces the eigenvalues of the observable $U$ is 
$\CHSH_U$, where the superscript $d$ means that the rules of this game depends on $d$.
Intuitively, this is one step towards verifying Alice and Bob use $\paulix{d}$ and $\pauliz{d}$ in their operator solution.

@@

%------------------------------------------------------------------------
\subsection{The single value test}
%------------------------------------------------------------------------
By the following test, we want to make sure that some unitary $U$ has eigenvalue $1$.
In this test $X = \{\ast\}$, $Y = \{0,1,\ast\}$, $A = \{\diamond, \perp\}$ and $B = \{0,1, \diamond, \perp\}$.
The scoring rules are
\begin{itemize}
	\item \textbf{Case 1} $x = y = \ast$: Alice and Bob should answer with $a, b \in \{\diamond, \perp\}$ and 
	they score only if $a = b$;
	\item \textbf{Case 2} $x =\ast$ and $y = 0$: when Alice answer $\diamond$, Bob should answer $0$, when 
	Alice answer$\perp$ all answers of Bob are accepted;
	\item \textbf{Case 3} $x = \ast$ and $y = 1$: when Alice answer $\diamond$, Bob should answer $0$, when 
	Alice answer$\perp$ all answers of Bob are accepted.
\end{itemize}

Define the subspace $V = \spn\{ \ket{u_0} \}$.
The ideal strategy has projective measurement 
\begin{align*}
&A_\ast^\diamond = B_\ast^\diamond= \ketbra{u_0}{u_0}, 
&&A_\ast^\perp = B_\ast^\perp = \1 - \ketbra{u_0}{u_0},\\
&B_0^0|_V = B_1^0|_V = \ketbra{u_0}{u_0}, 
&&B_0^1|_V = B_1^1|_V = 0.
\end{align*}
The shared state is 
\begin{align}
	\ket{\psi} = \frac{1}{\sqrt{d}} \sum_{i \in [d]} \ket{u_i}\ket{u_i}.
\end{align}
Note that the shared state is the same as the one used in the extended weighted CHSH game.
So are the observables $B_0$ and $B_1$.

It is easy to calculate the ideal correlation, which is
\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c||c|c|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{} &
\multicolumn{2}{|c|}{$y=\ast$} &
\multicolumn{2}{|c|}{$y=0$} &
\multicolumn{2}{|c|}{$y=1$}\\
\cline{3-8}
\multicolumn{2}{|c|}{} &$b = \diamond$ & $b = \perp$ & $b = 0$ & $b = 1$ & $b = 0$ & $b = 1$\\
\hline
\hline
\multirow{2}{*}{$x = \ast$} & $a=\diamond$ & $1/d$ & 0 & $1/d$ & 0 & $1/d$ & 0 \\
\cline{2-8}
&$a=\perp$ & 0 & $(d-1)/d$ & \small $\pr{\perp0}{\ast0}$ & \small $\frac{d-1}{d} -\pr{\perp0}{\ast0}$  
& \small $\pr{\perp0}{\ast1}$ & \small $\frac{d-1}{d}- \pr{\perp0}{\ast0}$  \\
\hline
\end{tabular}
\caption{Ideal correlation of the single value test.}
\end{center}
\end{table}
The reason we have $y=0$ or $y=1$ is that we want Bob to reuse operators from $\LS$ and we want to
conclude that $B_0B_1$ has eigenvalue $1$.

\begin{lemma}
	\label{lm:svt_comp}
	If a quantum strategy$(\{\tA_\ast^a\}_a, \{\{\tB_y^b\}_b\}_y, \ket{\tpsi}$ has the same behaviour as
	the optimal one, then $(\tB_0^0 - \tB_0^1)(\tB_1^0-\tB_1^1)$ has eigenvalue $1$.
\end{lemma}
\begin{proof}
By the marginal distribution we know that $\| A_\ast^\diamond \ket{\psi}\| = \frac{1}{\sqrt{d}}$.
From the condition that $P(\diamond 0|\ast 0) = 1/d$, we know
\begin{align}
	\frac{  \bra{\psi} \tA_\ast^\diamond  \tB_0^0 \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|^2} = 1,
\end{align}
which implies that 
\begin{align}
 \tB_0^0 \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} = \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|}.
\end{align}
With similar reasoning, we get
\begin{align}
 \tB_1^0 \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} = \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|}.
\end{align}
Hence $ \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} $ is in the intersection of $\supp(\tB_0^0)$ and $\supp(\tB_1^0)$.
Since $\supp(\tB_y^0)$ and $\supp(\tB_y^1)$ are disjoint, we know
\begin{align*}
	(\tB_y^0 - \tB_y^1)  \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|}  =  \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} - 0 = \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} 
\end{align*}
for $y = 0,1$.
Therefor, we know $ \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} $ is an eigenvector of $\tB_0\tB_1$ with eigenvalue $1$ because
\begin{align}
	\tB_0\tB_1 \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} = \tB_0 \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} =  \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|}.
\end{align}
\end{proof}
In the later section, when we apply this test to make sure some unitary $U$ has eigenvalue $1$, 
we denote the test by $\SVT_U$.

@@

With appropriate substitutions, the rest of the proof follows the same derivation as that in Appendix A of Ref.~\cite{bamps2015},
so we omit it here.
\end{proof}
%=====================================
\section{Construction of $\Gamma(\LS)$}
\label{sec:construct}
%=====================================
In this section, we are going to embed the group $\Pg_{\LS}$ into a solution group $\Gamma(\LS)$ of a linear system game.
What we do is to write any generator with arbitrary order as a product of new order-$2$ generators and rewrite all
the relations with the new generators. In the end, we can get rid of the generators $y_i$ and $u$ and all 
the remaining generators are order-$2$.

>>>>

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{EPR^{(#1)}}
\newcommand{\paulix}[1]{\sigma_x^{(#1)}}
\newcommand{\pauliz}[1]{\sigma_z^{(#1)}}
\newcommand{\G}[1]{G^{(#1)}}
\newcommand{\LS}{LS}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}

@@

\title{Self-test prime dimensional EPR pairs with constant alphabet}

@@

The main tool to understand linear system game is through its solution group over $\Z_d$.
\begin{definition}[Solution group over $\Z_d$ \cite{coladan2017}]
	For the linear system game associated with $Ax = b$ over $\Z_d$, its solution group $\Gamma(A,b,\Z_d)$ has 
	one generator for each variable and one relation for each equation and relations enforcing that the variables in the same
	equation commutes. The set of local commutativity relations is denoted by $R_c$ and defined by
	\begin{align}
		R_c := \set{ [x_i, x_j] |  A_{li} \neq 0 \neq A_{lj} \text{ for some } 1 \leq l \leq m}.
	\end{align}
	The set of constraint satisfaction relations is denoted by $R_{eq}$ and defined by.
	\begin{align}
		R_{eq} := \set{ \J^{-b(l)} \Pi_{i=1}^n  x_i^{A_{li}} | 1\leq l\leq m}
	\end{align}
	Then the solution group has presentation 
	\begin{align}
	\Gamma(A,b,\Z_d) := \ip{ \{x_i\}_{i=1}^n \cup \{\J\} : R_c \cup R_{eq} \cup \{ (x_i)^d, \J^d| 1 \leq i \leq n\}}. 
	\end{align}
\end{definition}
Note that the relations $(x_i)^d$ and $\J^d$ ensure that we have solutions over $\Z_d$.
Then the operator solution of $\Gamma(A,b,\Z_d)$ is given below.
\begin{definition}[Operator solution]
	An operator solution for the linear system game associated with $Ax =b$ over $\Z_d$ is a unitary representation
	$\tau$ of $\Gamma(A,b,\Z_d)$ such that $\tau(\J) = \omega_d\1$. A conjugate operator solution is a unitary 
	representation mapping $\J$ to $\overline{\omega_d}\1$.
\end{definition}
What has been established in Ref.\cite{cleve2017,coladan2017} is that we can construct a perfect strategy of a
linear system game from its operator solution and vice versa.
%========================================
\section{Components of $\G{d}$}
%========================================
Suppose we would like to self-test $\ket{\EPR{d}}$ with $\G{d}$, where $d$ is prime and has primitive root $2$.
Later we will see how to deal with general prime numbers and why there are infinitely many prime dimensional EPR pairs 
that can be self-tested by a variant of $\G{d}$.
%----------------------------------------------------------------
\subsection{The linear system game}
%----------------------------------------------------------------
The main component of $\G{d}$ is a linear system game $\LS$, whose solution group is derived from the 
following group
\begin{align}
	\Pg_{\LS} = \langle u, x : uxu^{-1} = x^2 \rangle.
\end{align}
%\begin{align}
%	\Pg_d = \langle x, z, \J : x^d = z^d = \J^d = e, zxz^{-1}x^{-1} = \J, x\J x^{-1}\J^{-1}= z\J z^{-1}\J^{-1} = e\rangle. 
%\end{align}
%The goal of our modification is to construct $\Pg_{\LS}$ which has implicit $d$-dependence.
%We first introduce new generators $u_x$ and $u_z$ to $\Pg_d$, and replace the relation $x^d = z^d = e$ 
%by the following relations
%\begin{align}
%\label{eq:sim}
%	u_x x u_x = x^2, \quad
%	u_z z u_z = z^2.
%\end{align}
%Consequently, the $d$ dependency of $\G{d}$ comes from constraints imposed by other components of the game,
%\footnote{Figuring out what $a$ is will take us one step closer to resolving Artin's Conjecture\cite{murty1988}.}
%but the alphabet sizes are determined by $\Pg_{\LS}$ and we will see why they are constant.
%Next, we drop the relation $\J^d = e$ and make the value of $\J$ determined by $x$ and $z$ in the 
%relation $xzx^{-1}z^{-1} = \J$.
%
%It can be easily checked that $\paulix{d}$ and $\pauliz{d}$ can be extended to a representation of $\Pg_{\LS}$ 
%where  $\paulix{d}$ and $\pauliz{d}$ are defined by
%\begin{align}
%	\paulix{d} = \sum_{i=0}^{d-1} \ketbra{i+1 \pmod{d} }{i}  \quad \quad
%	\pauliz{d} = \sum_{i=0}^{d-1} \omega_d^i \ketbra{i}{i}.
%\end{align}
%Moreover, if $U_x\paulix{d}U_x^\dagger = (\paulix{d})^2$ and $U_z\pauliz{d}U_z^\dagger = (\pauliz{d})^2$,
%we can verify that 
%\begin{align}
%	U_xU_z = \1 = U_zU_x,
%\end{align}
%Hence, we do not need both $u_x$ and $u_z$ as generators and we just need one of them.
%In the end, we define $\Pg_{\LS}$ by
%\begin{equation}
%\begin{aligned}
%	\Pg_{\LS} =  \langle x, z, u, \J :  &zxz^{-1}x^{-1} = \J, [x,\J]=[z,\J]=[u,\J] = e, \\
%	&uxu^{-1} = x^2, u^{-1}zu = z^2 \rangle. 
%\end{aligned}
%\end{equation}
%This group will be embedded in a solution group, $\Gamma(\LS)$, following Slofstra's embedding techniques.
%The corresponding game $\LS$ has $n = 2351$ variables and $m= 1916$ equations.
See Appendix~\ref{sec:construct} for details.
%------------------------------------------------------------------------
\subsection{The extended weighted CHSH game}
%------------------------------------------------------------------------
The extended weighted CHSH game is added to make sure that some of Alice and Bob's observables have
eigenvalues $\omega_d$ and $\omega_d^{d-1}$.
The notation for the extended weighted CHSH game that enforces the eigenvalues of the observable $U$ is 
$\CHSH_U$, where the superscript $d$ means that the rules of this game depends on $d$.
Intuitively, this is one step towards verifying Alice and Bob use $\paulix{d}$ and $\pauliz{d}$ in their operator solution.

@@

%------------------------------------------------------------------------
\subsection{The single value test}
%------------------------------------------------------------------------
By the following test, we want to make sure that some unitary $U$ has eigenvalue $1$.
In this test $X = \{\tri \}$, $Y = \{0,1,\tri\}$, $A = \{\diamond, \perp\}$ and $B = \{0,1, \diamond, \perp\}$.
The scoring rules are
\begin{itemize}
	\item \textbf{Case 1} $x = y = \tri$: Alice and Bob should answer with $a, b \in \{\diamond, \perp\}$ and 
	they score only if $a = b$;
	\item \textbf{Case 2} $x =\tri$ and $y = 0$: when Alice answer $\diamond$, Bob should answer $0$, when 
	Alice answer$\perp$ all answers of Bob are accepted;
	\item \textbf{Case 3} $x = \tri$ and $y = 1$: when Alice answer $\diamond$, Bob should answer $0$, when 
	Alice answer$\perp$ all answers of Bob are accepted.
\end{itemize}

Define the subspace $V = \spn\{ \ket{u_0} \}$.
The ideal strategy has projective measurement 
\begin{align*}
&A_\tri^\diamond = B_\tri^\diamond= \ketbra{u_0}{u_0}, 
&&A_\tri^\perp = B_\tri^\perp = \1 - \ketbra{u_0}{u_0},\\
&B_0^0|_V = B_1^0|_V = \ketbra{u_0}{u_0}, 
&&B_0^1|_V = B_1^1|_V = 0.
\end{align*}
The shared state is 
\begin{align}
	\ket{\psi} = \frac{1}{\sqrt{d}} \sum_{i \in [d]} \ket{u_i}\ket{u_i}.
\end{align}
Note that the shared state is the same as the one used in the extended weighted CHSH game.
So are the observables $B_0$ and $B_1$.

It is easy to calculate the ideal correlation, which is
\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c||c|c|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{} &
\multicolumn{2}{|c|}{$y=\tri$} &
\multicolumn{2}{|c|}{$y=0$} &
\multicolumn{2}{|c|}{$y=1$}\\
\cline{3-8}
\multicolumn{2}{|c|}{} &$b = \diamond$ & $b = \perp$ & $b = 0$ & $b = 1$ & $b = 0$ & $b = 1$\\
\hline
\hline
\multirow{2}{*}{$x = \tri$} & $a=\diamond$ & $1/d$ & 0 & $1/d$ & 0 & $1/d$ & 0 \\
\cline{2-8}
&$a=\perp$ & 0 & $(d-1)/d$ & \small $\pr{\perp0}{\tri0}$ & \small $\frac{d-1}{d} -\pr{\perp0}{\tri0}$  
& \small $\pr{\perp0}{\tri1}$ & \small $\frac{d-1}{d}- \pr{\perp0}{\tri0}$  \\
\hline
\end{tabular}
\caption{Ideal correlation of the single value test.}
\end{center}
\end{table}
The reason we have $y=0$ or $y=1$ is that we want Bob to reuse operators from $\LS$ and we want to
conclude that $B_0B_1$ has eigenvalue $1$.

\begin{lemma}
	\label{lm:svt_comp}
	If a quantum strategy$(\{\tA_\tri^a\}_a, \{\{\tB_y^b\}_b\}_y, \ket{\tpsi}$ has the same behaviour as
	the optimal one, then $(\tB_0^0 - \tB_0^1)(\tB_1^0-\tB_1^1)$ has eigenvalue $1$.
\end{lemma}
\begin{proof}
By the marginal distribution we know that $\| A_\tri^\diamond \ket{\psi}\| = \frac{1}{\sqrt{d}}$.
From the condition that $P(\diamond 0|\tri 0) = 1/d$, we know
\begin{align}
	\frac{  \bra{\psi} \tA_\tri^\diamond  \tB_0^0 \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|^2} = 1,
\end{align}
which implies that 
\begin{align}
 \tB_0^0 \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} = \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|}.
\end{align}
With similar reasoning, we get
\begin{align}
 \tB_1^0 \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} = \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|}.
\end{align}
Hence $ \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} $ is in the intersection of $\supp(\tB_0^0)$ and $\supp(\tB_1^0)$.
Since $\supp(\tB_y^0)$ and $\supp(\tB_y^1)$ are disjoint, we know
\begin{align*}
	(\tB_y^0 - \tB_y^1)  \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|}  =  \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} - 0 = \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} 
\end{align*}
for $y = 0,1$.
Therefor, we know $ \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} $ is an eigenvector of $\tB_0\tB_1$ with eigenvalue $1$ because
\begin{align}
	\tB_0\tB_1 \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} = \tB_0 \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|} =  \frac{\tA_\tri^\diamond \ket{\psi}}{\| \tA_\tri^\diamond \ket{\psi}\|}.
\end{align}
\end{proof}
In the later section, when we apply this test to make sure some unitary $U$ has eigenvalue $1$, 
we denote the test by $\SVT_U$.

%=====================================
\section{Main result}
\label{sec:main}
%=====================================
%-----------------------------------------------------------------
\subsection{The game $\G{d}$}
%-----------------------------------------------------------------
Assume the linear system game has $n$ variables and $m$ equations.
Alice receives $x \in \{1,\dots m+4 \}$ and Bob receives
$y \in \{1,\dots,n+2\}$. The scoring rules are the following:
\begin{itemize}
	\item when $x \in \{1,\dots m\}$ and $y \in \{1, \dots n\}$, they are scored according to the 
	linear system game, $\LS$;
	\item when $x \in \{m+1, m+2, m+3\}$ and $y \in \{1, 2, n+1\}$, they are scored according to $\CHSH_X$,
	where 
	\begin{align}
		&\ast_A = m+1, \quad 0_A = m+2,\quad 1_A = m+3,\\
		&\ast_B = n+1,\quad 0_B = 1, \quad 1_A = 2,
	\end{align}
	are the inputs for the game $\CHSH_X$
	(The intuition behind is that $B_1B_2 = X$.);
	\item when $x = m+4$ and  $y \in \{1,2,n+2\}$, they are scored according to $\SVT_X$, where
	\begin{align}
		& \tri_A = m+4 \\
		& \tri_B = n+2, \quad 1_B = 1,\quad 2_B = 2
	\end{align}
	are the inputs for the game $\SVT_X$;
	\item otherwise, they score $0$.
\end{itemize}
Note that the dimension $d$ is defined in the rules of $\CHSH_X$.
Next we are going to prove that the strategy winning this game optimally can self-test $d$-dimensional EPR pair.

%-----------------------------------------------------------------
\subsection{Proof}
%-----------------------------------------------------------------
\hl{This subsection needs to be formalized.}
By Lemma~$4.3$ of \cite{coladan2017}, we can extract an operator solution from the perfect winning strategy 
of the linear system game: 
For each variable $\{ x_i \}_{i=1}^n$, Alice and Bob has operators $A_i$ and $B_i$ respectively.
The condition that they agree with assignment to variables means that 
\begin{align}
	\bra{\psi} A_i \otimes \overline{B_i} \ket{\psi} = 1 \Rightarrow A_i \otimes \overline{B_i} \ket{\psi} = \ket{\psi}
\end{align}
and the condition that Alice's assignments satisfy the constraint means that 
\begin{align}
	\Tr(\rho_A \Pi_{j: A_{ij} \neq 0} A_j) = \Tr(\rho_A) \text{ for all } 1 \leq i \leq m
\end{align}
where $\rho_A =  \Tr_B(\ketbra{\psi}{\psi})$, so for  any $\ket{v} \in \supp(\rho_A)$,
we have 
\begin{align}
\Pi_{j:A_{ij} \neq 0} A_j \ket{v} = \ket{v} \text{ for all } 1 \leq i \leq m.
\end{align}
Since the relation $u^{-1}xu = x^2$ is embedded in this linear system game, we know
\begin{align}
	\sigma_A(u)^\dagger A_1A_2 \sigma_A(u) \ket{v}= (A_1A_2)^2 \ket{v} \text{ for all } \ket{v} \in \supp(\rho_A).
\end{align}
For simplicity, we define $X = A_1A_2$ and $U = \sigma_A(u)$.
For simplicity, we define $X = A_1A_2$ and $U = \sigma_A(u)$.
The condition becomes
\begin{align}
	UXU^\dagger \ket{v} = X^2 \ket{v} \text{ for all } \ket{v} \in \supp(\rho_A).
\end{align}
On the subspace $\supp(\rho_A)$, we have the equality
\begin{align}
	\label{eq:sim}
	UXU^\dagger X^{-2} = \1.
\end{align}
We will come back to the implication of this condition later.

Suppose the support of $\tA_\ast^\diamond$ is spanned by $\ket{u_0}$ and $\ket{u_1}$ and 
define $\ket{x_1} = 1/\sqrt{2}(\ket{u_0} + i\ket{u_1})$. 
The test $\CHSH_X$ tells that $\ket{x_1}$ is the eigenvector of $X$ with eigenvalue $e^{i\pi/d} = \omega_d$.
Similarly, define $\ket{x_{d-1}} = 1/\sqrt{2}(\ket{u_0} - i\ket{u_1})$ such that $X \ket{x_{d-1}} = \omega_d^{d-1}\ket{x_{d-1}}$.
We know 
\begin{align}
	\tA_\ast^\diamond \ket{\tpsi} = \tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi} = \frac{1}{\sqrt{d}} (\ket{u_0}\ket{u_0} + \ket{u_1}\ket{u_1}).
\end{align}
If we restrict to Alice's system, we get 
\begin{align}
	\Tr_B(\tA_\ast^\diamond \ketbra{\tpsi}{\tpsi} \tA_\ast^\diamond) =\tA_\ast^\diamond \rho_A \tA_\ast^\diamond = 
 \frac{1}{d} \ketbra{u_0}{u_0} + \ketbra{u_1}{u_1} = \frac{1}{d} \tA_\ast^\diamond.
\end{align}
Hence $\rho_A$ acts as $\1$ on $\supp(\tA_\ast^\diamond)$.
We also know that there exists local unitary $U_A$ such that 
\begin{align}
U_A \tA_\ast^\diamond U_A^\dagger = \ketbra{x_1}{x_1}+\ketbra{x_{d-1}}{x_{d-1}}
\end{align}
and 
\begin{align}
\Tr(\ketbra{x_1}{x_1} \rho_A)
=\Tr(U_A \ketbra{u_0}{u_0} U_A^\dagger \rho_A) 
= \frac{1}{d} \Tr(U_A\ketbra{u_0}{u_0} U_A^\dagger) 
= \frac{1}{d},
\end{align}
and similarly $\Tr( \ketbra{x_{d-1}}{x_{d-1}}\rho_A) = 1/d$.

Next, we calculate the eigen-decomposition of $X$ in $\supp(\rho_A)$.
Based on \cref{eq:sim}, we know
\begin{align}
\label{eq:ladder}
 XU^\dagger \ket{x_1} = U^\dagger X^2 \ket{x_1} = \omega_d^2 U^\dagger \ket{x_1},
\end{align}
so $U^\dagger \ket{x_1}$ is an eigenvector of $X$ with eigenvalue $\omega_d^2$.
By induction, we know $X (U^\dagger)^i \ket{x_1} = \omega_d^{2^i} (U^\dagger)^i\ket{x_1}$. 
From the set $\{(U^\dagger)^i \ket{x_1}\}_{i=0}^{d-2}$, we can identify $\ket{x_i}$ for $i = 1 \dots  d-1$
such that $X \ket{x_i} = \omega_d^i \ket{x_i}$.
From the single value test, we know 
\begin{align}
	\tA_\triangle^\diamond \ket{\tpsi} = \tA_\triangle^\diamond \x \tB_\triangle^\diamond \ket{\tpsi} = \frac{1}{\sqrt{d}}
	\ket{x_0}\ket{x_0}
\end{align}
where $X \ket{x_0} = \ket{x_0}$. 
The effect of $\CHSH_X$ and $\SVT_X$ is that we have a set $\{ \ket{x_i} \}_{i \in [d]} \in \supp(\rho_A)$ such that
\begin{align}
	X \ket{x_i} = \omega_d^i \ket{x_i}.
\end{align}
The other effect of $\SVT_X$ is that we know 
\begin{align}
	\tA_\triangle^\diamond \rho_A \tA_\triangle^\diamond = \frac{1}{d} \ketbra{x_0}{x_0} = \frac{1}{d} \tA_\triangle^\diamond.
\end{align}
\hl{\textbf{Question}: Can we show $\Tr(\ketbra{x_2}{x_2} \rho_A) = 1/d$?}

@@

With appropriate substitutions, the rest of the proof follows the same derivation as that in Appendix A of Ref.~\cite{bamps2015},
so we omit it here.
\end{proof}
%=====================================
\section{Construction of $\Gamma(\LS)$}
\label{sec:construct}
%=====================================
%In this section, we are going to embed the group $\Pg_{\LS}$ into a solution group $\Gamma(\LS)$ of a linear system game.
%What we do is to write any generator with arbitrary order as a product of new order-$2$ generators and rewrite all
%the relations with the new generators. In the end, we can get rid of the generators $y_i$ and $u$ and all 
%the remaining generators are order-$2$.
%
%We first embed the relation $xzx^{-1}z^{-1} = \J$ in a linear system game very similar to the Magic Square game.
%It has been shown that the following relations embeds $xzx^{-1}z^{-1} = \J$ \footnote{For example, Fig.~$11$ of Ref.~\cite{coladan2017}
%proves it in a group picture.}. Let $y_3 = z$ and $y_7 = x$ and the linear relations are 
%\begin{align*}
%	&y_1y_2y_3 = e,
%	&&y_4y_5y_6 = e,
%	&&y_7y_8y_9 = e,\\
%	&y_1^{-1}y_4^{-1}y_7^{-1} = e,
%	&&y_2^{-1}y_5^{-1}y_8^{-1} = \J,
%	&&y_3^{-1}y_6^{-1}y_9^{-1} = e.
%\end{align*}
%We refer to these set of linear relations as the $\MS_l$ relations.
%The magic square game also introduces some commutation relations:
%\begin{align*}
%	&[y_1, y_2] = [y_1, y_3] = [y_1, y_4] = [y_1,y_7] = e,\\
%	&[y_2, y_3] = [y_2, y_5] = [y_2, y_8] = e,\\
%	&[y_3, y_6] = [y_3, y_9] = e,\\
%	&[y_4, y_7] = [y_4,y_5] =  [y_4,y_6] = e, \\
%	& [y_5,y_6] =  [y_5,y_8] = e,\\
%	& [y_6,y_9] = e,\\
%	& [y_7,y_8] =  [y_7,y_9] = e,\\
%	&[y_8,y_9] = e.
%\end{align*}
%The set of the commutation relations above is denoted by $\MS_c$.
%So we redefine $\Pg_{\LS}$ as 
%\begin{align}
%	\Pg_{\LS} = \langle \{y_i\}_{i=1}^9,u,\J: \MS_l \cup \MS_c \cup \{ [\J, y_i] = [\J, u] = e,
%					uy_7u^{-1} = y_7^2, u^{-1}y_3u = y_3^2\}	 \rangle.
%\end{align}
%Then we can use a procedure similar to the one used in the proof of Proposition~$4.8$ of Ref.~\cite{slofstra2017} to 
%embed $\Pg_{\LS}$ into a group with only order-$2$ generators except for $\J$, whose order is implicit.
%
%We start by introducing $y_{3,1}$ and $y_{3,2}$ of order $2$ such that $y_3 = y_{3,1}y_{3,2}$ 
